---
title: 'Vignette: tweets-class'
output:
  rmdformats::material:
    self_contained: true
    fig_width: 6
    fig_height: 6
    thumbnails: FALSE
    highlight: haddock
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# rtweet

## Package Philosophy

Coming from the communication field---where there is an abundance of critical and analytical thinking and a shortage of computer programming---it's important to me that anyone interested in researching Twitter can feel relatively comfortable approaching data collected via Twitter's APIs.  

Accordingly, the philosophy behind `rtweet` is simple. It is to make Twitter data more accessible to more people. 

```
rtweet philosophy: make Twitter data more accessible to more people.
```

After talking with my Computing and Statistics professor, I think I've narrowed in on some things about `rtweet` I want to keep simple and clear. Unfortunately for the R-nerd in me, that means---at least, for the time being---giving up on S4 classes and methods. While new classes and methods would have been cool, I don't think it would have added a lot of functionality. And, if anything, I think it would have detracted from the central purpose of rtweet, which I described above.

So, I've created this document for two reasons. First, because I wanted to communicate the philosophy behind the package. Second, because I wanted to send off my S4 work in style. And what better way is there to say goodbye than to say it on a classy rmarkdown vignette.


## Classes

```{r rtweet}
library(rtweet)
mk <- get_favorites("kearneymw", n = 2000)

# create object of tweets class
mk_s4 <- make_tweets(mk)
class(mk_s4)

# print (show) method for tweets
mk_s4

# plot method for tweets
plot(mk_s4)

# another example
tw <- search_tweets("rstats", n = 500, dev = TRUE)
tw
plot(tw)
```

The plot is clearly gratuitous, but it was just supposed to be a placeholder. I think I'll store these classes in the package for now and maybe revisit the idea down the road, but they won't be integrated into functions any time soon.
