---
title: "Collecting Twitter Data"
output:
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Collecting Twitter Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, comment = "#>", collapse = TRUE)
```

This vignette provides a quick tour of the R package.

```{r}
library("rtweet")
```


## Authenticate

First you should set up your own credentials, this should be done just once ever:

```{r, eval=FALSE}
auth_setup_default()
```

Which will look up your account on your browser and create a token and save it as default.
From now on, on this R session on others we can use this authentication with:

```{r, eval=FALSE}
auth_as("default")
```

Automatically rtweet will use that token in all the API queries it will do in the session.

If you want to set up a bot or collect a lot of information, please read the `vignette("auth", "rtweet")`.

```{r child, echo=FALSE, results='asis'}
file <- system.file("child.Rmd", package = "rtweet", mustWork = TRUE)
res <- knitr::knit_child(file, 
                         options = list(eval = TRUE, collapse = TRUE, 
                                        error = TRUE, base.dir = getwd()), 
                         quiet = TRUE)
cat(res, sep = '\n')
```
